Do We Judge Children's Books by Their Covers? 

### 2024-12-04 paper/paper.qmd
Grammar check and fix

---
title: "Do We Judge Children's Books by Their Covers? "
subtitle: "Exploring Title, Exclamation Marks, and Reviewer Bias"
author: 
  - David Qi
thanks: "Code and data are available at: https://https://github.com/UTDQi/children_book_review"
date: today
date-format: long
abstract: "This study examines the impact of first impressions on children's book ratings, focusing on how attributes such title, page count, and review count influence ratings. Using data from Goodreads and both simple linear regression and fine-tuned transformer models, we found that book titles alone explained 7.94% of the variation in ratings, indicating the significance of first impressions. This study provide support for previous studies in concluding that children may favor the theme of excitement and celebration, which are useful in building recommendation system and selecting optimal titles."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

# Introduction {#sec-intro}
The rise of user-generated content has transformed how consumers interact with media, especially when it come to book ratings. These ratings serve as an indirect reflection of a book's quality and readers' perceptions, serving as one of the few pieces of information that help potential readers to form initial impressions. As they play a irreplaceable role in guiding decisions, consequently, it has become standard practice to use book ratings as a predictor variable in recommendation systems, serving as a key indicator of how much a reader enjoys a book.

However, children's books, as a unique genre, present distinct dynamics in the realm of user-generated ratings and recommendation systems. Unlike adult literature, children rarely contribute directly to ratings or reviews. Instead, parents, educators, and caregivers typically provide feedback. Which have made is difficult to create recommendation systems [@judgecover]. And since many reviewer are not direct reader of the book, we hypothesize their rating may subject to greater bias from first impression.

@@

This paper made use of simple linear regression models and fine-tuned pretrained transformer models, by analyzing children's book data from Goodreads[@goodreaddata1;@goodreaddata2], to uncover how much such first impression will influence the rating of a book. The study provides guidance for author and publishers to create attractive titles, identifies traits in children's book rating, which may be useful for designing recommendation systems. Where these recommendation systems, when it comes to children, may be difficult to create due to lack of user generated data, and will likely benefit from understanding provided by this study.

@@

The R scripts in this paper are written in R[@citeR], The table in our study are generated by knitr [@knitr],  and graph with ggplot2[@ggplot2]. Data input and output were done using arrow[@arrow].Data manipulation made use of tidyverse[@tidyverse]. The data download, cleaning and transformer model made use of python[@citePython] with supporting packages pytorch[@NEURIPS2019_9015], Scikit-learn[@pedregosa2011scikit], transformers[@wolf-etal-2020-transformers], tqdm[@tqdm], numpy[@harris2020array], pandas[@mckinney2010data], requests[@requests].

@@

# Data {#sec-data}
We will be using the children's book data from goodreads.com, collected in late 2017, originally for the propose of academic research conducted by @goodreaddata1 and @goodreaddata2. We would also thank @tellingstories's book for providing information on this dataset.

## Overview
The children's book dataset contains 124,082 books. After removing books that lacks the requires information, or that have incorrect entries easily identifiable(such as having June 31 as date), we have selected 65,118 books for analysis. The justification and risks of such selection will be discussed in [Discussion](#).

## Data Measurement
Goodreads is an American book recommendation and social networking platform. Its primary purpose is to allow users to catalog their books, keep track of their reading progress, share reviews, and engage in discussions about literature. The included books are mainly in English, with some books in other languages available. Any registered user on Goodreads may give rating to any book, the rating comes in integers from 1 to 5, with no half-star option. Along with a rating, user also may write text reviews for the book, which may be seen by other users. Descriptions of a book were updated by volunteer and staffs that maintains the website, while the rating contents are user generated.

One issue this may raise is as each user has different understand of rating, the aggregate effect may lower the effectiveness of rating's role as a estimand for satisfaction.

The data collection was done through a web-scarping on contents available for any user[@goodreaddata1;@goodreaddata2].

@@

### Average Rating
[@fig-ratingoverview] displays the distribution of average book ratings('average_rating'), which appears to approximate a normal distribution centered around 3.88. The data suggests a tendency for people to give higher ratings. An average book will not receive a 3, but will have average rating close to 3.88 instead.

@@

### Publication Day
Publication day(`publication_day`) is the day in the month the book is published, it is used to capture monthly trends. Such pattern do exists, as [@fig-pub_day_overview] clearly shows that there is a great increase in book published one the first day of each month, and a slight rise the fifteenth day. We would expect the difference in level of competition between different days in a month can influence people's perception toward a book.

@@

### Publication Day In The Year
Publication Day In The Year(`publication_day_in_year`) is the day in the year the book is published, it is used to capture yearly trends. Similar to previous part, [@fig-pub_day_yearly_overview] is a bar chart that shows the yearly pattern on publication of books. We Observe a decline in book sales in June and December, and peaks in January and Sepetember.

@@

### Publication Year
Publication Year is the year the book is published, people may treat old books differently from new books in the way they give reviews. Also as [@fig-pub_year_overview] shows, there is an exponential increase in the number of books people can choose form. The drop in the end of the graph is because that many newly published books need time for then to gain their first rating, and the book published in 2018 haven't been published at the time of data collection and naturally don't have reviews. 
```{r}
#| label: fig-pub_year_overview
#| fig-cap: Distribution of Publication Year
#| include: true
#| echo: false
#| warning: false
#| message: false

@@

### Number of Text Reviews
Number of text reviews (`text_reviews_count`) is the number of written text reviews for a book. The number of text reviews is visible to new readers, and provides them with a first impression for the popularity of the book. [@fig-textreview] shows the distribution of books with different number of text reviews, note that this is not a full plot as there are very few books that received far more than 1000 reviews, the most being 31,536 reviews. We see that of most book getting very few review and a few book have very high reviews.

@@

### Text Reviews To Rating Ratio
Text Reviews To Rating Ratio (`text_reviews_ratio`) is the ratio between number of text review and number of ratings. It serves as a measurement of reader engagement and the atmosphere of the reader community. Which can have substantial impact on one's impression of a book.  [@fig-textreviewratio] shows the distribution of books with different number of this ratio, showing readers have different level of engagement for different books. Note this variable displays a weak correlation of 0.211 with year of publication, including this variable in the model will minimize the effect of year of publication in the linear regression model. However we have included both variables in consideration for interpretiblity.

@@

ggplot(book_data, aes(x = as.numeric(text_reviews_ratio))) + 
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    x = "Text Review/Ratings Ratio",
    y = "Count(Books)"
  ) +
  theme_minimal()
```
### Title
Title (`title`) is the most visible trait on the front cover of a book. The wording of the title will directly shape one's first impression of the book, and directly determines if one have interest in the book. Which have made it very suitable for our propose, as it may be the variable that has the greatest impact on first impression. However, as a text variable, it may not be easy and require complicated model to process title data.

### Number of pages
Number of Pages (`num_pages`) is the sometimes more notable than the title of the book, one often realize how thick a book is without knowing the title. If we want to evaluate the impact of first impression on book reviews, number of pages is an important factor to take into consideration. [@fig-num_pages_overview] shows that most books in the dataset have a low number of pages, as the number of pages increases, the frequency of books with higher page counts drops off significantly. Agreeing with our impression of children;s book.

@@

```
## Unused Varibles
There are certain variables that could be drawn from the dataset, which may fit the topic of this paper, but will not be used for modeling. In this section we justify why they are not selected.

### Publication Month
The effect of publication Month have been fully covered by days in a year. While the latter is more accurate.

### Rating Count
The total number of ratings is an important indicator of book popularity. However including it does not improve the model by much, and it can be captured by text review to rating ratio, along with number of text reviews. So we did not inculde the varible for simplicity.

@@

## Transformer Model
To analysis how title may affect the rating of a book, we use a transformer model to process the title. To implement this model, we used python[@citePython] with supporting packages pytorch[@NEURIPS2019_9015], Scikit-learn[@pedregosa2011scikit], transformers[@wolf-etal-2020-transformers], tqdm[@tqdm], numpy[@harris2020array], and pandas[@mckinney2010data].

@@

We will fine tune the BERT model to predict average rating from the book title. A book title is a string input, which first passes through BERT pretrained tokenizer to be made into a sequence of tokens. For example the title "Bradford Street Buddies : Springtime Blossoms" will become:\
$$
\text{
[CLS], bradford, street, buddies, : , spring, -time, blossoms, [SEP], [PAD], [PAD]
}\
$$
Where [CLS] is special token for "class", [SEP] is special token for “separator”, and [PAD] is special token for “padding”. The pretrained BERT model accept this tokenized input and outputs a token-wise embeddings tensor that encodes meaning and information related to each token as it learned from pretrained data. As BERT have been pretrained on massive data, the embedding it produces has real connections with Semantic and Syntactic meaning of the token. While the embedding related to the [CLS] token carries information regarding the overall meaning of the title[@devlin2019bert;@diveintodeeplearning].

For our specific use, we need to fine-tune the model. Which is preformed by adding a fully connected layer after the output related to [CLS], then train the resulting model with this new layer added, @fig-bert from original paper of @devlin2019bert  illustrated this process when the task is classification. In this case we are replacing the classification fully connected layer by a regression layer. Fine tuning BERT for regression tasks is also a common practice, with examples demonstrated by people such as @diveintodeeplearning and @pharmaceutics14081710.

@@

We use a 70%,15%,15% train,validation,test separation. We train the model on training data with mean squared error loss on validation set to measure model performance. We then adjust the learning rate, number of epoch trained, and batch size until we find a optimal hyperparameter that produces the best model on validation data. 
We then choose this model for further discussion.

@@

[@tbl-model] are the model coefficients fitted. The model have adjusted R-squared 0.038, showing the model have limited predictive power. However, the F-statistic(426 on 6 and 65111 Degrees of Freedom) and Pr(>|t|) provide concrete evidence that these first impression variables that we draw out have influence on average rating. Discussion of each variable is in the [Discussion ](@sec-discussion) section.

@@

### Linear Regression
The linear regression model constructed using numerical data have provide many interesting findings around each variables. And have pointed out directions for future research: using experiment and surveys to verify the causation we have proposed. However there are many limitations to linear regression model, the underlying assumptions need to be fulfilled, it have difficulties processing text data such as titles, which is why we proposed using BERT model for a more thorough analysis of this data.

@@

#### Publication Day 
Although the change per day is small, it is highly significant. This suggests that books published later in the calendar year (closer to December) might receive slightly higher ratings on average. The relationship is positive, but the effect size is quite small. This possibly reflect the high competition on the first day of each month have damaged rating for book published on that day.

#### Number of Pages
For each additional page in a book, the average rating increases by 0.000616.
Books with more pages tend to have slightly higher average ratings. This suggests that readers might associate longer books with higher quality, that they may tend to believe the book is more in depth, more rigorous and is of higher value. We may also link this to the psychological phenomenon of cognitive dissonance, where some people may tend persuade themselves to believe the book is good to revolve the discomfort of purchasing something that is worthless [@festinger1959cognitive].

@@

#### Text Reviews Ratio
For each 1% increase in the ratio of text reviews to total reviews, the average rating increases by 0.0801.
This is one of the most influential variables in the model. Books that have a higher ratio of text reviews and more detailed feedback from readers tend to receive significantly higher ratings. Indicating that detailed text-based reviews are more strongly associated with higher ratings than numerical ratings. We could also explain association by the positive impression created through higher engagement.

@@

### BERT Model
The fine tuned BERT model have provided understanding on our starting question: how much do people judge a book by its cover? Our answer is that by title alone, we can explain 7.94% of the variance. While the model can be used to provide guidance in creating individual titles. It may also be experimented to see the overall effect of having one type of title over another.

For example, our experiment of replacing periods with exclamation marks have aligned with the result of @judgecover, who find that "young children are inclined towards joy, favoring books including terms like celebration, excitement, gratitude, cheerful, and smile". Which are hinted by the use of exclamation marks. This has reinforced our previous understanding of the subject, and further verifies the predictions of our model. 
While the lowered rating by removing "the" may come from the resulting grammatical error in some books. There are other similar experiments one can do with this model to further develop knowledge on how wording of the title affect reader perception. One example would be replacing masculine pronouns into feminine or neutral pronouns, and observe the effect it has on average rating. And alternative testing preformed by removing the exclamation marks and replacing them with period could be conducted.

@@

### Correlation Versus Causation
In the paper we have observed various Correlations, however, they may not demonstrate a causation. For example, we attempts to explain variation in score by text reviews ratio, however there is a important potential confounder variable, which we are not investigating since the nature of research is to find relation of first impression to ratings. This confounder variable is the quality of the book, a high quality book will naturally receive positive reviews, and may potentially attract people to comment more on the book. Where in the case of number of pages, a very important variable that we do not have hold of is formatting, larger fonts may improve reader experience while resulting in pages. 
A more comprehensive study that, likely in form of a survey may be applied to uncover causation, and whether our explanation are accurate.

### Missing Data
There are certain important facts about the book that highly link to first impression that we can't acquire form this dataset.Including fonts, page size and paper quality.

Also around half of of the data point are removed due to missing or incorrect data. As there may be systematic trends to what data are missing(e.g. data for popular books are less likely to be wrong since more people concerns about it), removing these data may have systematically introduced bias into our data.

### Sources of Bias.
There may be other sources of data not from the data cleaning process. An an American website, Goodread is not representative for books in other languages than English. Not only are the books of these languages, the readers from other cultures may not be well represented. Which increase this bias further. 
Also there may be economical and technological source of bias. Books that are more accessible or affordable to readers in the U.S.  may dominate the data. Titles from smaller publishers or independent authors, particularly those outside of major Western markets, may not receive the same level of visibility or reviews.
While since the data is form an online platform, it only allow data collection on people who have the money and skill to access such platforms. Which will exclude many of the young children and elderly. As well as views from people in poverty. 
Further research could be targeted specifically toward these groups. In fact, as @judgecover points out, there are many existing, "state of the art" recommendation algorithm designed for adults. However, similar algorithms experience difficulties to be implemented on children, as there are not similar amount of data available. This lack of data have increased the importance further research through traditional methods such as surveys. See [Appendix 1](@appendix1) for a discussion on how such survey could be conducted.

@@

1. A letter explaining the propose, theme and length and possible questions of the survey.

@@

3. Selection of any book or book series with market price less than 30$. Which will be mailed within 30 days of completing the survey questionnaire.

These incentives matches the outline given by @stantcheva2023surveys. And may incentivize the participants to provide more accurate replies.

@@

The survey questions will be grouped logically, for children it will covering the topics below:

@@

For adults, the "reading practices" section will be replaces by a section collecting the participant's experience with children's book. And the Understanding of Rating will be from a adult perspective, asking questions such as "Will you write reviews based on your chlidren's fondness of the book?"

@@

[@fig-diagnostics] are the model diagnostics for the model. Q-Q plot is generally acceptable. There are certain influential points in the data set, however, these points does not occur incorrectly and result of some very popular books, so we are not removing them from the data set. There are some potential violation of linear regression assumptions visible from the residue vs. fitted plot, however we will accept this model for now since we have better model available and this only serves as a help in interpreting the numerical varibles.

>>>>

---
title: "Do We Judge Children's Books by Their Covers? "
subtitle: "Exploring Title, Exclamation Marks, and Reviewer Bias"
author: 
  - David Qi
thanks: "Code and data are available at: https://github.com/UTDQi/children_book_review"
date: today
date-format: long
abstract: "This study examines the impact of first impressions on children's book ratings, focusing on how attributes such title, page count, and review count influence ratings. Using data from Goodreads and both simple linear regression and fine-tuned transformer models, we found that book titles alone explained 7.94% of the variation in ratings, indicating the significance of first impressions. This study provide support for previous studies in concluding that children may favor the theme of excitement and celebration, which are useful in building recommendation system and selecting optimal titles."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

# Introduction {#sec-intro}
The rise of user-generated content has transformed how consumers interact with media, especially when it comes to book ratings. These ratings serve as an indirect reflection of a book's quality and readers' perceptions, serving as one of the few pieces of information that help potential readers to form initial impressions. As they play a irreplaceable role in guiding decisions, consequently, it has become standard practice to use book ratings as a predictor variable in recommendation systems, serving as a key indicator of how much a reader enjoys a book.

However, children's books, as a unique genre, present distinct dynamics in the realm of user-generated ratings and recommendation systems. Unlike adult literature, children rarely contribute directly to ratings or reviews. Instead, parents, educators, and caregivers typically provide feedback. Which have made is difficult to create recommendation systems [@judgecover]. And since many reviewers are not direct reader of the book, we hypothesize their rating may subject to greater bias from first impression.

@@

This paper made use of simple linear regression models and fine-tuned pretrained transformer models, by analyzing children's book data from Goodreads [@goodreaddata1;@goodreaddata2], to uncover how much such first impression will influence the rating of a book. The study provides guidance for author and publishers to create attractive titles identifies traits in children's book rating, which may be useful for designing recommendation systems. Where these recommendation systems, when it comes to children, may be difficult to create due to lack of user generated data, and will likely benefit from understanding provided by this study.

@@

The R scripts in this paper are written in R [@citeR], the tables in our study are generated by knitr [@knitr], and graph with ggplot2 [@ggplot2]. Data input and output were done using arrow [@arrow].Data manipulation made use of tidyverse[@tidyverse]. The data download, cleaning and transformer model made use of python [@citePython] with supporting packages pytorch[@NEURIPS2019_9015], Scikit-learn [@pedregosa2011scikit], transformers [@wolf-etal-2020-transformers], tqdm[@tqdm], numpy[@harris2020array], pandas [@mckinney2010data], requests [@requests].

@@

# Data {#sec-data}
We will be using the children's book data from goodreads.com, collected in late 2017, originally for the purpose of academic research conducted by @goodreaddata1 and @goodreaddata2. We would also thank the book "Telling Stories with Data" for providing information on this dataset [@tellingstories].

## Overview
The children's book dataset contains 124,082 books. After removing books that lacks the required information, or that have incorrect entries easily identifiable (such as having June 31 as date), we have selected 65,118 books for analysis. The justification and risks of such selection will be discussed in [Discussion](#sec-discussion).

## Data Measurement
Goodreads is an American book recommendation and social networking platform. Its primary purpose is to allow users to catalog their books, keep track of their reading progress, share reviews, and engage in discussions about literature. The included books are mainly in English, with some books in other languages available. Any registered user on Goodreads may give rating to any book. The rating comes in integers from 1 to 5, with no half-star option. Along with a rating, user also may write text reviews for the book, which may be seen by other users. Descriptions of a book were updated by volunteer and staffs that maintains the website, while the rating contents are user generated.

One issue this may raise is as each user has different understood of rating, the aggregate effect may lower the effectiveness of rating's role as an estimand for satisfaction.

The data collection was done through a web-scarping on contents available for any user [@goodreaddata1; @goodreaddata2].

@@

### Average Rating
[@fig-ratingoverview] displays the distribution of average book ratings ('average_rating'), which appears to approximate a normal distribution centered around 3.88. The data suggests a tendency for people to give higher ratings. An average book will not receive a 3, but will have average rating close to 3.88 instead.

@@

### Publication Day
Publication day (`publication_day`) is the day in the month the book is published, it is used to capture monthly trends. Such pattern do exists, as [@fig-pub_day_overview] clearly shows that there is a great increase in book published one the first day of each month, and a slight rise the fifteenth day. We would expect the difference in level of competition between different days in a month can influence people's perception toward a book.

@@

### Publication Day in The Year
Publication Day in The Year (`publication_day_in_year`) is the day in the year the book is published, it is used to capture yearly trends. Similar to previous part, [@fig-pub_day_yearly_overview] is a bar chart that shows the yearly pattern on publication of books. We Observe a decline in book sales in June and December, and peaks in January and September.

@@

### Publication Year
Publication Year is the year the book is published, people may treat old books differently from new books in the way they give reviews. Also as [@fig-pub_year_overview] shows, there is an exponential increase in the number of books people can choose form. The drop in the end of the graph is because that many newly published books need time for them to gain their first rating, and the book published in 2018 haven't been published at the time of data collection and naturally don't have reviews. 
```{r}
#| label: fig-pub_year_overview
#| fig-cap: Distribution of Publication Year
#| include: true
#| echo: false
#| warning: false
#| message: false

@@

### Number of Text Reviews
Number of text reviews (`text_reviews_count`) is the number of written text reviews for a book. The number of text reviews is visible to new readers, and provides them with a first impression for the popularity of the book. [@fig-textreview] shows the distribution of books with different number of text reviews, note that this is not a full plot as there are very few books that received far more than 1000 reviews, the most being 31,536 reviews. We see that of most book getting very few review and a few books have very high reviews.

@@

### Text Reviews to Rating Ratio
Text Reviews to Rating Ratio (`text_reviews_ratio`) is the ratio between number of text review and number of ratings. It serves as a measurement of reader engagement and the atmosphere of the reader community, which can have substantial impact on one's impression of a book.  [@fig-textreviewratio] shows the distribution of books with different number of this ratio, showing readers have different level of engagement for different books. Note this variable displays a weak correlation of 0.211 with year of publication, including this variable in the model will minimize the effect of year of publication in the linear regression model. However we have included both variables in consideration for interpretiblity.

@@

ggplot(book_data, aes(x = as.numeric(text_reviews_ratio))) + 
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    x = "Text Review/Ratings Ratio",
    y = "Count(Books)"
  ) +
  theme_minimal()
```

### Title
Title (`title`) is the most visible trait on the front cover of a book. The wording of the title will directly shape one's first impression of the book, and directly determines if one have interest in the book, which has made it a very suitable predictor to be included in our research, since it is the variable that has the greatest impact on first impression. However, as a text variable, it may not be easy and require complicated model to process title data.

### Number of pages
Number of Pages (`num_pages`) is the sometimes more notable than the title of the book, one often realize how thick a book is without knowing the title. If we want to evaluate the impact of first impression on book reviews, number of pages is an important factor to take into consideration. [@fig-num_pages_overview] shows that most books in the dataset have a low number of pages, as the number of pages increases, the frequency of books with higher page counts drops off significantly. Agreeing with our impression of children’s book.

@@

```
## Unused Variables
There are certain variables that could be drawn from the dataset, which may fit the topic of this paper, but will not be used for modeling. In this section we justify why they are not selected.

### Publication Month
The effects of publication Month have been fully covered by days in a year, while the latter is more accurate.

### Rating Count
The total number of ratings is an important indicator of book popularity. However including it does not improve the model by much, and it can be captured by text review to rating ratio, along with number of text reviews. So we did not include the variable for simplicity.

@@

## Transformer Model
To analysis how title may affect the rating of a book, we use a transformer model to process the title. To implement this model, we used python [@citePython] with supporting packages pytorch [@NEURIPS2019_9015], Scikit-learn [@pedregosa2011scikit], transformers [@wolf-etal-2020-transformers], tqdm [@tqdm], numpy [@harris2020array], and pandas [@mckinney2010data].

@@

We will fine tune the BERT model to predict average rating from the book title. A book title is a string input, which first passes through BERT pretrained tokenizer to be made into a sequence of tokens. For example the title "Bradford Street Buddies: Springtime Blossoms" will become:\
$$
\text{
[CLS], bradford, street, buddies, : , spring, -time, blossoms, [SEP], [PAD], [PAD]
}\
$$
Where [CLS] is special token for "class", [SEP] is special token for “separator”, and [PAD] is special token for “padding”. The pretrained BERT model accept this tokenized input and outputs a token-wise embeddings tensor that encodes meaning and information related to each token as it learned from pretrained data. As BERT has been pretrained on massive data, the embedding it produces has real connections with Semantic and Syntactic meaning of the token. While the embedding related to the [CLS] token carries information regarding the overall meaning of the title [@devlin2019bert; @diveintodeeplearning].

For our specific use, we need to fine-tune the model. Which is performed by adding a fully connected layer after the output related to [CLS], then train the resulting model with this new layer added, @fig-bert from original paper of @devlin2019bert  illustrated this process when the task is classification. In this case we are replacing the classification fully connected layer by a regression layer. Fine tuning BERT for regression tasks is also a common practice, with examples demonstrated by researchers such as @diveintodeeplearning and @pharmaceutics14081710.

@@

We use a 70%,15%,15% train,validation,test separation. We train the model on training data with mean squared error loss on validation set to measure model performance. We then adjust the learning rate. Number of epoch trained, and batch size until we find an optimal hyperparameter that produces the best model on validation data. 
We then choose this model for further discussion.

@@

[@tbl-model] are the model coefficients fitted. The model have adjusted R-squared 0.038, showing the model have limited predictive power. However, the F-statistic (426 on 6 and 65111 Degrees of Freedom) and P values provide concrete evidence that these first impression variables that we draw out have influence on average rating. Discussion of each variable is in the [Discussion](@sec-discussion) section.

@@

### Linear Regression
The linear regression model constructed using numerical data have provided many interesting findings around each variable. And have pointed out directions for future research: using experiment and surveys to verify the causation we have proposed. However there are many limitations to linear regression model, the underlying assumptions need to be fulfilled, it have difficulties processing text data such as titles, which is why we proposed using BERT model for a more thorough analysis of this data.

@@

#### Publication Day 
Although the change per day is small, it is highly significant. This suggests that books published later in the calendar year might receive slightly higher ratings on average. The relationship is positive, but the effect size is small. This possibly reflect the high competition on the first day of each month have damaged rating for book published on that day.

#### Number of Pages
For each additional page in a book, the average rating increases by 0.000616.
Books with more pages tend to have slightly higher average ratings. This suggests that readers might associate longer books with higher quality, which they may tend to believe the book is more in depth, more rigorous and is of higher value. We may also link this to the psychological phenomenon of cognitive dissonance, where some people may tend persuade themselves to believe the book is good to revolve the discomfort of purchasing something that is worthless [@festinger1959cognitive].

@@

#### Text Reviews Ratio
For each 1% increase in the ratio of text reviews to total reviews, the average rating increases by 0.0801.
This is one of the most influential variables in the model. Books that have a higher ratio of text reviews and more detailed feedback from readers tend to receive significantly higher ratings, indicating that detailed text-based reviews are more strongly associated with higher ratings than numerical ratings. We could also explain association by the positive impression created through higher engagement.

@@

### BERT Model
The fine-tuned BERT model have provided understanding on our starting question: how much do people judge a book by its cover? Our answer is that by title alone, we can explain 7.94% of the variance. While the model can be used to provide guidance in creating individual titles, it may also be experimented to see the overall effect of having one type of title over another.

For example, our experiment of replacing periods with exclamation marks have aligned with the result of @judgecover, they found that "young children are inclined towards joy, favoring books including terms like celebration, excitement, gratitude, cheerful, and smile", which are hinted by the use of exclamation marks. This has reinforced our previous understanding of the subject, and further verifies the predictions of our model.

While the lowered rating by removing "the" may come from the resulting grammatical error in some books, there are other similar experiments one can do with this model to further develop knowledge on how wording of the title affect reader perception. One example would be replacing masculine pronouns into feminine or neutral pronouns, and observe the effect it has on average rating. And alternative testing performed by removing the exclamation marks and replacing them with period could be conducted.

@@

### Correlation versus Causation
In the paper we have observed various Correlations. However, they may not demonstrate causation. For example, we attempts to explain variation in score by text reviews ratio, however there is an important potential confounder variable, which we are not investigating since the nature of research is to find relation of first impression to ratings. This confounder variable is the quality of the book. A high quality book will naturally receive positive reviews, and may potentially attract people to comment more on the book. Where in the case of number of pages, a very important variable that we do not have hold of is formatting, larger fonts may improve reader experience while resulting in pages.

A more comprehensive study likely in form of a survey may be applied to uncover causation, and whether our explanations are accurate.

### Missing Data
There are certain important facts about the book that highly link to first impression that we can't acquire form this dataset. Including fonts, page size and paper quality.

Also around half of the data points are removed due to missing or incorrect data. As there may be systematic trends to what data are missing (e.g. data for popular books are less likely to be wrong since more people concerns about it), removing these data may have systematically introduced bias into our data.

### Sources of Bias.
There may be other sources of data not from the data cleaning process. An American website, Goodread is not representative for books in other languages than English. Not only are the books of these languages, the readers from other cultures may not be well represented, which increase this bias further.

Also there may be economical and technological source of bias. Books that are more accessible or affordable to readers in the U.S may dominate the data. Titles from smaller publishers or independent authors, particularly those outside of major Western markets, may not receive the same level of visibility or reviews.

Since the data is form an online platform, it only allows data collection on people who have the money and skill to access such platforms, which will exclude many of the young children and elderly, as well as views from people in poverty.

Further research could be targeted specifically toward these groups. In fact, as @judgecover points out, there are many existing, "state of the art" recommendation algorithm designed for adults. However, similar algorithms experience difficulties to be implemented on children, as there are not similar amount of data available. This deprivation of data has increased the importance further research through traditional methods such as surveys. See [Appendix 1](@appendix1) for a discussion on how such survey could be conducted.

@@

1. A letter explaining proposes, theme and length and possible questions of the survey.

@@

3. Selection of any book or book series with market price less than 30$, which will be mailed within 30 days of completing the survey questionnaire.

These incentives matches the outline given by @stantcheva2023surveys, and may incentivize the participants to provide more accurate replies.

@@

The survey questions will be grouped logically, for children it will cover the topics below:

@@

For adults, the "reading practices" section will be replaces by a section collecting the participant's experience with children's book. And the Understanding of Rating will be from an adult perspective, asking questions such as "Will you write reviews based on your chlidren's fondness of the book?"

@@

[@fig-diagnostics] are the model diagnostics for the model. Q-Q plot is generally acceptable. There are certain influential points in the data set, however, these points does not occur incorrectly and result of some very popular books, so we are not removing them from the data set. There are some potential violations of linear regression assumptions visible from the residue vs. fitted plot. However we will accept this model for now since we have better model available and this only serves as a help in interpreting the numerical variables.
